Supplemental Materials: \emph{Simultaneous segmentation and registration of diffusion MR images of the brain driven by active-contours}

### 2015-02-20 Publications/2015-NeuroImage/04-methods.tex
add supplementals

\paragraph*{Settings, implementation details, and evidencing convergence}
\label{sec:conv_report}
The registration parameters (such as $\tau$, the multi-resolutions on the B-Spline grid,
  target image smoothing, etc.) and implementation details (for instance the sparse matrix approach
  to fast interpolation) are dicussed in the {\color{red} Supplemental Materials, section XX.XX}.
The actual choice of parameter settings are publicly distributed with the source code of the experiments.
Additionally, we release our software along with a tool for generating convergence reports to
  demonstrate the behavior of the tool and help scientists configure their experiments.
A sample of report is found in the {\color{red} Supplemental Materials, section XX.XX}.

>>>>

\paragraph*{Settings, implementation details, and convergence}
\label{sec:conv_report}
The registration parameters (such as $\tau$, the B-Spline grid resolutions,
  target image smoothing, etc.) and implementation details (for instance the sparse matrix approach
  to fast interpolation) are dicussed in the \suppl{}, {\color{red} section S1}.
The actual choice of parameter settings are publicly distributed with the source code of the experiments.
Additionally, we release our software along with a tool for generating convergence reports to
  demonstrate the behavior of the tool and help scientists configure their experiments.
A sample of report is found in the \suppl{} {\color{red}, section S1.3}.

### 2015-02-20 Publications/2015-NeuroImage/05-results.tex
add supplementals

\paragraph*{Assessing the segmentation model}\label{sec:res_model_and_metric} %
%
Preliminarly, we investigated the aptness of our segmentation model to play as cost function
  driving the registration process.
First, we evaluated several alternative models to segment the target bivariate images
  (\gls*{fa} and \gls*{adc}).
Based on the observed joint distribution of each (see {\color{red} Supplemental Materials, ...}),
  we selected the 6-regions scheme described in \nameref{sec:human_connectome}.

>>>>

\paragraph*{Assessing the segmentation model}\label{sec:res_model_and_metric} %
%
Preliminarly, we investigated the aptness of our segmentation model to play as cost function
  driving the registration process.
First, we evaluated several alternative models to segment the target bivariate images
  (\gls*{fa} and \gls*{adc}).
Based on the observed joint distribution of each (\suppl{}, {\color{red} section S2}),
  we selected the 6-regions scheme described in \nameref{sec:human_connectome}.
